|

### 2020-05-25 paper/Manuscript.Rmd
update 2020-05-25 19:52:55

authornote: |
  This is a preprint, not a peer-reviewed publication. Comments, contributions,
  and coauthors are welcome. Please contact the lead author.
  Acknowledgements: Jeroen Ooms (feedback, suggesting gert, and using Remotes
  field).
keywords          : "open science; reproducibility; r; dynamic document generation; version control"
wordcount         : "5921"

@@

The R-package `worcs` automate most steps of the workflow
for R users.
Several arguments support the choice to implement this workflow in R.
First, R and all of it extensions are free open source software, which
should be the tool of choice for open science.
Second, as of this writing, R is the most advanced programming language in terms
of the implementation of tools required for an open science workflow.
Third, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper.
Fourth, R is well-supported; a vibrant online community exists for R, developing new R methods and packages, and providing support and tutorials for existing ones.
Finally, R is highly interoperable:
Packages are available to load nearly every imaginable filetype, and output can be written to most file types, including DOCX and PDF (in APA style), and HTML format. 
Moreover, wrappers are available for many tools developed in other programming languages, and code written in other programming languages can be evaluated from R, including C++, 
Fortran, and Python [@allaireMarkdownPythonEngine]. There are excellent free
resources for learning R, such as the book R for Data Science [@grolemundDataScience2017].

>>>>

authornote: |
  This is a preprint, not a peer-reviewed publication. Comments, contributions,
  and coauthors are welcome. Please contact the lead author.
  We acknowledge Jeroen Ooms for offering feedback and suggesting gert.
keywords          : "open science; reproducibility; r; dynamic document generation; version control"
wordcount         : "8257"

@@

The R-package `worcs` automate most steps of the workflow
for R users.
Several arguments support the choice to implement this workflow in R.
First, R and all of it extensions are free open source software, which
should be the tool of choice for open science.
Second, as of this writing, R is the most advanced programming language in terms
of the implementation of tools required for an open science workflow.
Third, R is the second-most cited statistical software package [@muenchenPopularityDataScience2012], following SPSS, which has no support for any of the open science tools discussed in this paper.
Fourth, R is well-supported; a vibrant online community exists for R, developing new R methods and packages, and providing support and tutorials for existing ones.
Finally, R is highly interoperable:
Packages are available to load nearly every imaginable filetype, and output can be written to most file types, including DOCX and PDF (in APA style), and HTML format. 
Moreover, wrappers are available for many tools developed in other programming languages, and code written in other programming languages can be evaluated from R, including C++, 
Fortran, and Python [@allaireMarkdownPythonEngine2020]. There are excellent free
resources for learning R, such as the book R for Data Science [@grolemundDataScience2017].
